Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-25 main_paper.tex

\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{%
  All authors: Department of Economics, Iowa State University.
  260 Heady Hall, Ames, IA 50011.
  Bartalotti: \protect\url{bartalot@iastate.edu};
  Calhoun: \protect\url{gcalhoun@iastate.edu} and
  \protect\url{http://gray.clhn.org};
  He: \protect\url{yanghe@iastate.edu}. Source code for the Monte Carlo
  experiments and empirical component of this paper are available online
  at \protect\url{https://github.com/grayclhn/boot-rd}. We would like to
  thank Matias Cattaneo, Juan Carlos Escanciano, seminar participants at
  the Advances in Econometrics conference on Regression Discontinuity
  Designs, and especially the two anonymous referees for helpful and
  substantive help and advice on earlier versions of this paper.}}

>>>>

\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{%
  All authors: Department of Economics, Iowa State University.
  260 Heady Hall, Ames, IA 50011.
  Bartalotti: \protect\url{bartalot@iastate.edu};
  Calhoun: \protect\url{gcalhoun@iastate.edu} and
  \protect\url{http://gray.clhn.org};
  He: \protect\url{yanghe@iastate.edu}. Source code for the Monte Carlo
  experiments and empirical component of this paper are available online
  at \protect\url{https://github.com/grayclhn/boot-rd}. We would like to
  thank Matias Cattaneo, Juan Carlos Escanciano, Sebastian Calonico, Max Farrell, Helle Bunzel, Brent Kreider, Quentin Brummet, seminar participants at
  the Advances in Econometrics conference on Regression Discontinuity
  Designs, Third Annual Conference of the International Association for Applied Econometrics,
 2016 North American Summer Meeting of the Econometric Society and the $69^{th}$ European Meeting of the Econometric Society, and especially the two anonymous referees for
  substantial help and advice on earlier versions of this paper.}}

### 2016-08-25 reply_2/cover_letter.tex

>>>>

Regarding referee 1's comments,
\begin{itemize}
\item (placeholder)
\end{itemize}
Regarding referee 2's comments.
\begin{itemize}
\item (placeholder)
\end{itemize}
We have also made the small notational changes and new definitions
the referees requested.

In addition, we discovered a small error in the simulation results ---
instead of reporting each estimator's bias, we reported the negative
bias. Since the values were close to zero, this does not have a
substantive effect on the results but we have, of course, fixed the
tables.
